Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-02-23 reports/rmarkdown/03_integrated_datasets.Rmd
add metadata association and KEGG for TRX

Ftest <- sapply(metadata_parameters,function(x){
  temp <- sapply(metadata_parameters,x=x,function(x,y){
    if (x==y){
      return( 1 )
    } else {
    f1 <- as.character(metadata[,x])
    f1[is.na(f1)] <- "NA"
    f1[f1==""] <- "NA"

    f2 <- as.character(metadata[,y])
    f2[is.na(f2)] <- "NA"
    f2[f2==""] <- "NA"

    f11 <- f1 [ (f1!="NA") & (f2!="NA") ]
    f22 <- f2 [ (f1!="NA") & (f2!="NA") ]
    contT1  <- table(f11,f22)
    print(x)
    print(y)
    return( fisher.test(contT1,simulate.p.value = T)$p.value )
    # return( chisq.test(contT1,simulate.p.value = T)$p.value )
    }
  })
  return(temp)
})

clean_Ftest <- Ftest
# clean_Ftest <- ( clean_Ftest + t(clean_Ftest) ) / 2
clean_Ftest <- -log10(clean_Ftest)
clean_Ftest[clean_Ftest > 5.5] <- 5.5
# clean_Ftest[ clean_Ftest > 0.05 ] <- 1

write.csv2(clean_Ftest , "../../results/metadata_association_results.csv",row.names = T)

>>>>

Ftest <- sapply(metadata_parameters,function(x){
  cat(paste0("\n",x,"\n"))
  temp <- sapply(metadata_parameters,x=x,function(x,y){
    if (x==y){
      return( 1 )
    } else {
      # if( !is.na(sum(as.numeric(metadata[,x]))) ){ f1 <- cut(as.numeric(metadata[,x]),breaks = 5 ) }
      if( is.numeric(metadata[,x]) ){ f1 <- cut(metadata[,x],breaks = 5 ) }
    f1 <- as.character(metadata[,x])
    f1[is.na(f1)] <- "NA"
    f1[f1==""] <- "NA"

    # if( !is.na(sum(as.numeric(metadata[,y]))) ){ f1 <- cut(as.numeric(metadata[,y]),breaks = 5 ) }
    if( is.numeric(metadata[,y]) ){ f2 <- cut(metadata[,y],breaks = 5 ) }
    f2 <- as.character(metadata[,y])
    f2[is.na(f2)] <- "NA"
    f2[f2==""] <- "NA"

    f11 <- f1 [ (f1!="NA") & (f2!="NA") ]
    f22 <- f2 [ (f1!="NA") & (f2!="NA") ]
    contT1  <- table(list(factor(f11,levels=unique(f1)),factor(f22,levels=unique(f2))))
    cat(".")
    f <- NULL
    try(f <- fisher.test(contT1,simulate.p.value = T),silent = T)
    if( is.null(f) ){ 
      return( 1  ) 
      } else {
      return( c(f$p.value)  ) 
    }
    # return( chisq.test(contT1,simulate.p.value = T)$p.value )
    }
  })

  return( temp )
})

clean_Ftest <- Ftest
# clean_Ftest <- ( clean_Ftest + t(clean_Ftest) ) / 2
clean_Ftest <- -log10(clean_Ftest)
clean_Ftest[clean_Ftest > 6] <- 6
# clean_Ftest[ clean_Ftest > 0.05 ] <- 1

write.csv2(Ftest , "../../results/metadata_association_results_complete.csv",row.names = T)
write.csv2(clean_Ftest , "../../results/metadata_association_results_filtered.csv",row.names = T)

### 2021-02-23 reports/rmarkdown/manuscript/manuscript_template.Rmd
add metadata association and KEGG for TRX

SNN_patients <- read.csv("../../../results/patient_SNN_graph.csv",row.names = 1)
SNN_bacteria <- read.csv("../../../results/bacteria_SNN_graph.csv",row.names = 1)
clean_Ftest <- read.csv2("../../../results/metadata_association_results.csv",row.names = 1)
datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=.6}
# Define Layout and set labels
layout(matrix(c(2 ,3,4,5,      6,7,17,17,          17,17,17,17,
                1,1,1,1,      1,8,17,17,          17,17,17,17,
                1,1,1,1,      1,9,18,18,         18,18,18,18,
                1,1,1,1,      1,10,19,19,         19,19,19,19,
                16,15,14,13,  12,11,20,20,         20,20,20,20 ) , ncol= 12,byrow = T),widths = 1,heights = c(1.2,1.2,1.2,1.2,1.2))
# layout.show(12)
figlabels <- letters

@@

par(mar=c(1,1,1,1))
for(j in sort(unique(bac_communities)) ){
  empty_plot()
  text( 0,1,labels = paste0(rownames(SNN_bacteria)[ bac_communities == j ],collapse = "\n"),adj=c(0,1),cex=.5)
  title(main=paste0("community",j),cex.main=.7)
}

@@

##############################################
# BACTERIAL COMMUNITY DIFFERENTIAL ABUNDANCE #
##############################################
module_means_per_dataset <- lapply(datasets_all_samples[-1],function(x){
  return( rowsum( x[rownames(SNN_bacteria),] , group = bac_communities ) / c(table(bac_communities)) )
})
# 
par(mar=c(1,10,1,6))
# for( j in c("ASV_tissue_V3_normalized_batch_corrected",
#         "ASV_CVL_V3_normalized_batch_corrected",
#         "ASV_CVL_V2_normalized_NOT_batch_corrected")){
#   temp_group <- as.character(group_annotation)
#   temp_group[ is.na(temp_group) ] <- "NA"
#   temp_group[ temp_group == "" ] <- "NA"
#   temp_group <- factor(temp_group)
#   
#   plot_dots(data=module_means_per_dataset[[j]],
#           genes=rownames(module_means_per_dataset[[j]]),col = pal,
#           clustering=temp_group, main=paste0("\n", sub("_norm.*","",j)))
# }
# add_letter(figlabels[1]); figlabels <- figlabels[-1]

plot_dots_difference(data = module_means_per_dataset[[2]],
                     data2 = module_means_per_dataset[[3]],
                     clustering = as.character(group_annotation),
                     clustering2 = as.character(group_annotation),
                     genes = rownames(module_means_per_dataset[[1]]),
                     main = "CVL3 vs CVL2",cex.row = .8)

plot_dots_difference(data = module_means_per_dataset[[2]],
                     data2 = module_means_per_dataset[[1]],
                     clustering = as.character(group_annotation),
                     clustering2 = as.character(group_annotation),
                     genes = rownames(module_means_per_dataset[[1]]),
                     main = "CVL3 vs tissue_V3",cex.row = .8)
# mypar(mar=c(2,2,2,6))
# plot(c(-2,10),c(-2,10),xaxs="i",yaxs="i")
# rrr <- rev(as.raster(colorRampPalette(c("blue","navy","grey95","firebrick","red"))(99)))
# rasterImage(as.raster(rrr),
#             xleft = par("usr")[2]+diff(par("usr")[1:2])/40,
#             xright = par("usr")[2]+diff(par("usr")[1:2])/20,
#             ybottom = par("usr")[4]-diff(par("usr")[1:2])/4,
#             ytop = par("usr")[4], 
#             interpolate = FALSE )
# text( c(par("usr")[2]+diff(par("usr")[1:2])/20,
#         par("usr")[2]+diff(par("usr")[1:2])/20) ,
#       c(par("usr")[4]-diff(par("usr")[3:4])/4,
#         par("usr")[4]),labels = c("min","max"),pos=4 )
# 
# 
# text( c(par("usr")[2]+diff(par("usr")[1:2])/20,
#         par("usr")[2]+diff(par("usr")[1:2])/20,
#         par("usr")[2]+diff(par("usr")[1:2])/20) ,
#       c(par("usr")[4]-diff(par("usr")[1:2])/4,
#         par("usr")[4]-diff(par("usr")[1:2])/8,
#         par("usr")[4]),labels = c("-1","0","+1"),pos=4 )
# text( c(par("usr")[2]+diff(par("usr")[1:2])/40) ,xpd=T,
#       c(par("usr")[4]+diff(par("usr")[3:4])/40),labels = c("Z-score"),adj=0 )

@@

@@

par(mar=c(4,.1,2,30))
barplot( rev(pvalues) , horiz = T , col= taxa_pal[factor(rev(module_color))],
         xaxs="i",yaxs="i",xlim=c(0,1.2*max(pvalues)),ylab="",xlab="-log10(pvalue)",las=1,names.arg = "")
points( rev(pvalues), seq(1,length(pvalues) )*1.2-.5,pch=21,bg=taxa_pal[factor(rev(module_color))] )
text( rev(pvalues)+1 , seq(1,length(pvalues) )*1.2-.5, adj=0,cex=.8,xpd=T,
      labels = rev(names(pvalues)),xpd=T)
text( rev(pvalues)+1 , seq(1,length(pvalues) )*1.2-.5, adj=0,cex=.8,
      labels = rev(sub(" [(].*","",names(pvalues)) ),col = paste0(taxa_pal[factor(rev(module_color))],90) ,xpd=T)
# text( rep(max(pvalues)+.5,length(pvalues)) , seq(length(pvalues),1 )*1.2-.5,
#       adj=0,cex=.8,labels = names(pvalues), col = taxa_pal[factor(module_color)] )

@@

@@

top_TRX_counts <- cpm(y)[top_dge, ]
top_TRX_counts <- t(apply(top_TRX_counts,1,function(x){scale(x,T,T)}))
top_TRX_counts[top_TRX_counts > 5] <- 5
colnames(top_TRX_counts) <- colnames(TRX_counts)

@@

@@

NESse_list <- read.csv2("../../../results/Hallmark_NESse_list.csv",row.names = 1)
NESse_list <- lapply(unique(sub("[.].*","",colnames(NESse_list))),function(x){
  temp <- NESse_list[ grep( x, colnames(NESse_list)) ]
  colnames(temp) <- sub(".*[.]","",colnames(temp))
  temp[is.na(temp)]<-0
  return(t(temp))
})
pvalue_list <- read.csv2("../../../results/Hallmark_pvalues_list.csv",row.names = 1)
pvalue_list <- lapply(unique(sub("[.].*","",colnames(pvalue_list))),function(x){
  temp <- pvalue_list[ grep( x, colnames(pvalue_list)) ]
  colnames(temp) <- sub(".*[.]","",colnames(temp))
  temp[is.na(temp)]<-0
  return(t(temp))
})
x <- pvalue_list[[1]]
df <- data.frame( pathway=c(sapply(1:ncol(x),x=x,function(i,x){rownames(x)} )),
                  bc=c(sapply(colnames(x),x=x,function(i,x){ rep(i,nrow(x)) }) ),
                  NES=c(NESse_list[[1]]),
                  abs_NES=abs(c(NESse_list[[1]])),
                  pvalue=c(x))
df <- df[df$pvalue!=0,]
df <- df[df$pvalue<0.05,]
df <- df[df$NES!=0,]

@@

mypar()
x <- NESse_list[[1]] - rowMeans( NESse_list[[1]] )
x [ pvalue_list[[1]] < 0.05 ] <- 0
x <- x[unique(top_per_bc$pathway),]
h <- hclust( as.dist( (1-cor(t(x)))/2 ) , method = "ward.D2" )
image( x[h$order,ncol(x):1],col=colorRampPalette(c("navy","grey95","firebrick"))(91),
       breaks=seq(-5,5,length.out = 92),
       axes=F,border=NA,xlab="",ylab="",line=.4,cex.main=1,font.main=1)
```

@@

for(i in c("ASV_CVL_V3_normalized_batch_corrected",
           "ASV_CVL_V2_normalized_NOT_batch_corrected",
           "ASV_tissue_V3_normalized_batch_corrected")){

  metadata_cor <- cor(t(module_means_per_dataset[[i]]),continuous_metadata,use = "pairwise.complete.obs")
  # metadata_cor_test <- cor.test(t(module_means_per_dataset[[i]]),continuous_metadata)

@@

  #add label
  add_letter(figlabels[1]); figlabels <- figlabels[-1]
}

par(mar=c(12,0,1,0))
image( t(metadata_cor [nrow(metadata_cor):1,]),axes=F,
         breaks = seq(-1,1,length.out = 90),main="",
         col=colorRampPalette(c("white"))(89) )
text(  0 ,seq(1,0,length.out = nrow(metadata_cor)) , 
  labels = rownames(metadata_cor), srt = 0, adj = c(0,.5), xpd = TRUE, cex=1)
```

@@

>>>>

SNN_patients <- read.csv("../../../results/patient_SNN_graph.csv",row.names = 1)
SNN_bacteria <- read.csv("../../../results/bacteria_SNN_graph.csv",row.names = 1)
clean_Ftest <- read.csv2("../../../results/metadata_association_results_complete.csv",row.names = 1)
datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=.6}
# Define Layout and set labels
layout(matrix(c(2 ,3,4,5,      6,7,17,17,          17,17,17,17,
                1,1,1,1,      1,8,17,17,          17,17,17,17,
                1,1,1,1,      1,9,18,18,         18,18,18,18,
                1,1,1,1,      1,10,19,19,         19,19,19,19,
                16,15,14,13,  12,11,20,20,         20,20,20,20 ) , ncol= 12,byrow = T),widths = 1,heights = c(1.2,1.2,1.2,1.2,1.2))
# layout.show(12)
figlabels <- letters
# 
# m <- matrix(as.character(c(1,2,3,4)),nrow = 2,ncol = 2)
# m
# m2 <- matrix(as.character(c(1,2,3,"m")),nrow = 2,ncol = 2)
# m2
# 
# matrix(c(1,2,j,3),nrow = 2,ncol = 2)
# layout_matrix <- function(data, nrow, ncol){
#   return( matrix(as.character(data), nrow = nrow, ncol = ncol)  )
# }
# layout_matrix2 <- function(data, nrow, ncol, widths=c(1,2), heights=c(2,3), res=res){
#   temp <- matrix(as.character(data), nrow = nrow, ncol = ncol)
#   widths <- rep(widths,ncol(temp))[1:ncol(temp)]
#   heights <- rep(heights,nrow(temp))[1:nrow(temp)]
#   
#   cumsum(widths)*100/sum(widths)
#   cumsum(heights)*100/sum(heights)
#   
#   temp2 <- matrix(1,nrow = nrow(data),ncol = ncol(data))
#   temp3 <- temp2 * heights
#   temp4 <- t( t( temp2 ) * widths ) 
#   temp2 <- matrix( "" , ncol = res , nrow = res )
#   
#   
#   for(i in 1:nrow(temp)){
#     for(j in 1:ncol(temp)){
#       temp2 <- 
#     }
#   }
#   temp <- apply(temp,1,function(x){rep( x , widths/ )})
#   return(   )
# }
# 
# m <- layout_matrix(c(1,2,3,4),2,2)
# m2 <- layout_matrix(c(1,2,3,"m"),2,2)

@@

par(mar=c(1,1,1,1))
for(j in sort(unique(bac_communities)) ){
  empty_plot()
  text( 0,1,labels = paste0(rownames(SNN_bacteria)[ bac_communities == j ],collapse = "\n"),adj=c(0,1),cex=.5)
  title(main=j,cex.main=.5)
}

@@

##############################################
# BACTERIAL COMMUNITY DIFFERENTIAL ABUNDANCE #
##############################################
module_means_per_dataset <- lapply(datasets_all_samples[-1],function(x){
  return( rowsum( x[rownames(SNN_bacteria),] , group = bac_communities ) / c(table(bac_communities)) )
})
# 
par(mar=c(2,10,2,6))
plot_dots_difference(data = module_means_per_dataset[[2]],
                     data2 = module_means_per_dataset[[3]],
                     clustering = as.character(group_annotation),
                     clustering2 = as.character(group_annotation),
                     genes = rownames(module_means_per_dataset[[1]]),
                     main = "CVL3 vs CVL2",cex.row = .8,srt=30)

plot_dots_difference(data = module_means_per_dataset[[2]],
                     data2 = module_means_per_dataset[[1]],
                     clustering = as.character(group_annotation),
                     clustering2 = as.character(group_annotation),
                     genes = rownames(module_means_per_dataset[[1]]),
                     main = "CVL3 vs tissue_V3",cex.row = .8,srt=30)

@@

saveRDS( y , "../../../results/Picrust_EdgeR_estimations.rds" )
write.csv2( top , "../../../results/Picrust_EdgeR_top_dge.csv" )

@@

par(mar=c(4,.1,2,20))
barplot( rev(pvalues) , horiz = T , col= taxa_pal[factor(rev(module_color))],
         xaxs="i",yaxs="i",xlim=c(0,1.2*max(pvalues)),ylab="",xlab="-log10(pvalue)",las=1,names.arg = "")
points( rev(pvalues), seq(1,length(pvalues) )*1.2-.5,pch=21,bg=taxa_pal[factor(rev(module_color))] )
text( rev(pvalues)+1 , seq(1,length(pvalues) )*1.2-.5, adj=0,cex=.8,xpd=T,
      labels = rev(names(pvalues)),xpd=T)
text( rev(pvalues)+1 , seq(1,length(pvalues) )*1.2-.5, adj=0,cex=.8,
      labels = rev(sub(" [(].*","",names(pvalues)) ),col = paste0(taxa_pal[factor(rev(module_color))],90) ,xpd=T)
# text( rep(max(pvalues)+.5,length(pvalues)) , seq(length(pvalues),1 )*1.2-.5,
#       adj=0,cex=.8,labels = names(pvalues), col = taxa_pal[factor(module_color)] )

@@

saveRDS( y , "../../../results/TRX_EdgeR_estimations.rds" )
write.csv2( top , "../../../results/TRX_EdgeR_top_dge.csv" )

@@

top_TRX_counts <- cpm(y,normalized.lib.sizes = T,log = T)[top_dge, ]
top_TRX_counts <- t(apply(top_TRX_counts,1,function(x){scale(x,T,T)}))
top_TRX_counts[top_TRX_counts > 5] <- 5
colnames(top_TRX_counts) <- colnames(TRX_counts)

@@

par(mar=c(4,.1,2,20))

plot( rev(as.dendrogram(h)) , xlim=c(max(h$height),-.2),horiz = T, leaflab = "none",xaxs="i",yaxs="i",axes=T,xlab="height")
# rect.dendrogram(rev(as.dendrogram(h)),h = 2,horiz = TRUE)
abline(v=cuttoff,xpd=F,col="red",lty=2)
points( rep(-.1,length(gene_module)),
        seq(length(gene_module),1,length.out = length(gene_module)),
        col=taxa_pal[factor(gene_module[h$order])],
        pch=16,cex=.5,xpd=T)

source("../enrichment_function.R")
gmt_list <- fgsea::gmtPathways("../../../supplementary_files/c2.cp.kegg.v6.2.symbols.gmt.txt")
res_list <- lapply( unique( gene_module[h$order] ),function(x){
  temp <- compute_enrichment(genes = names(gene_module)[gene_module==x],
                            gmt_list = gmt_list,
                            min_terms_pathway = 10,
                            max_terms_pathway = 300,
                            min_overlap = 3,
                            sort_by_pvalue = T)
  temp <- temp[!grepl("REGULATION",rownames(temp)),]
  return(temp)
} )
names(res_list) <- unique( gene_module[h$order] )

@@

NESse_list <- read.csv2("../../../results/Hallmark_NESse_list.csv",row.names = 1)
NESse_list <- lapply(unique(sub("[.].*","",colnames(NESse_list))),function(x){
  temp <- NESse_list[ grep( x, colnames(NESse_list)) ]
  colnames(temp) <- sub(".*[.]","",colnames(temp))
  temp[is.na(temp)]<-0
  return(t(temp))
})
pvalue_list <- read.csv2("../../../results/Hallmark_pvalues_list.csv",row.names = 1)
pvalue_list <- lapply(unique(sub("[.].*","",colnames(pvalue_list))),function(x){
  temp <- pvalue_list[ grep( x, colnames(pvalue_list)) ]
  colnames(temp) <- sub(".*[.]","",colnames(temp))
  temp[is.na(temp)]<-0
  return(t(temp))
})
x <- pvalue_list[[2]]
df <- data.frame( pathway=c(sapply(1:ncol(x),x=x,function(i,x){rownames(x)} )),
                  bc=c(sapply(colnames(x),x=x,function(i,x){ rep(i,nrow(x)) }) ),
                  NES=c(NESse_list[[1]]),
                  abs_NES=abs(c(NESse_list[[1]])),
                  pvalue=c(x))
df <- df[df$pvalue!=0,]
df <- df[df$pvalue<0.05,]
df <- df[df$NES!=0,]

@@

mypar(1,2,mar=c(4,10,2,4))
for(i in 1:2){
x <- NESse_list[[i]]
x [ pvalue_list[[i]] < 1 ] <- 0
x <- x[unique(top_per_bc$pathway),]
# h <- hclust( as.dist( (1-cor(t(x)))/2 ) , method = "ward.D2" )
# image( x[h$order,ncol(x):1],col=colorRampPalette(c("navy","grey95","firebrick"))(91),
#        breaks=seq(-5,5,length.out = 92),
#        axes=F,border=NA,xlab="",ylab="",line=.4,cex.main=1,font.main=1)

sizes <- pvalue_list[[i]]
sizes[sizes < 2] <- 0
sizes[sizes > 10] <- 10
sizes <- sizes / max(sizes)

plot( sort(rep(1:ncol(x),nrow(x))),
      rep(nrow(x):1,ncol(x)),
        col=colorRampPalette(c("navy","grey95","firebrick"))(91)[cut( c(x) , breaks = seq(-5,5,length.out = 92) )],pch=16 ,
      cex= sizes*2 + 0.2,
      axes=F,xlab="",ylab="", frame=T)
srt=30
text(1:ncol(x), par("usr")[3] - (par("usr")[4])/200, labels = colnames(x), srt = srt,
     adj = c(ifelse(srt==0,.5,ifelse(srt==90,1,1)),ifelse(srt==0,1,ifelse(srt==90,.5,1))),
     xpd = TRUE, cex=.6)
text(par("usr")[1] - (par("usr")[2])/200, 1:nrow(x) , labels = rownames(x), srt = 0, adj = c(1,0.5), xpd = TRUE, cex=.6)

add_scale_legend(pal = colorRampPalette(c("navy","grey95","firebrick"))(91),labels = c("-5","0","5"))
add_size_legend(labels = c("> 0.01","< 1e-6","< 1e-10"),max.cex = 2.2, min.cex = .2)
}

@@

for(i in c("ASV_CVL_V3_normalized_batch_corrected",
           "ASV_CVL_V2_normalized_NOT_batch_corrected",
           "ASV_tissue_V3_normalized_batch_corrected")){
  metadata_cor <- cor(t(module_means_per_dataset[[i]]),continuous_metadata,use = "pairwise.complete.obs")
  # metadata_cor_test <- cor.test(t(module_means_per_dataset[[i]]),continuous_metadata)

@@

  #add label
  add_letter(figlabels[1]); figlabels <- figlabels[-1]
}
par(mar=c(12,0,1,0))
image( t(metadata_cor [nrow(metadata_cor):1,]),axes=F,
         breaks = seq(-1,1,length.out = 90),main="",
         col=colorRampPalette(c("white"))(89) )
text(  0 ,seq(1,0,length.out = nrow(metadata_cor)) ,
  labels = rownames(metadata_cor), srt = 0, adj = c(0,.5), xpd = TRUE, cex=1)
```

## Figure S2 v2

for(k in c("ASV_CVL_V3_normalized_batch_corrected",
           "ASV_CVL_V2_normalized_NOT_batch_corrected",
           "ASV_tissue_V3_normalized_batch_corrected")){
res2 <- lapply( 1:nrow(module_means_per_dataset[[k]]),k=k, function(i,k){
  res <- lapply( c( colnames(clean_Ftest) , continuous_parameters ) , i=i,k=k,function(j,i,k) {
    model <- paste0("module_means_per_dataset[['",k,"']][",i,",] ~ ",j)
    m <- summary(lm( eval(parse(text=model)), data = metadata ))
    f <- m$fstatistic
    p <- pf(f[1],f[2],f[3],lower.tail=F)
    temp <- c(m$r.squared,m$adj.r.squared,m$fstatistic,p)
    return(temp)
  })
  res <- t(as.data.frame(res))
  rownames(res) <- c( colnames(clean_Ftest) , continuous_parameters )
  colnames(res) <- c("r.squared","adj.r.squared","F-statistic","df1","df2","pvalue")
  return(res)
})
names(res2) <- rownames(module_means_per_dataset[[k]])

pvals <- sapply(res2, function(x){x[,"pvalue"]})
rs <- sapply(res2, function(x){x[,"r.squared"]})

sizes <- -log10( pvals )
sizes[sizes < 2] <- 0
sizes[sizes > 11] <- 10
sizes <- sizes / max(sizes)

plot(0,0, las=1,xlim=c(.5,ncol(rs)+.5),ylim=c(.5,nrow(rs)+.5),
       axes=F,ylab="",xlab="",main=gsub("^ASV_|_norm.*","",k),xaxs="i",yaxs="i", frame=T)
for(i in 1:ncol(rs)){
  lines(c(i,i),c(nrow(rs)+.5,0),col="grey95",lwd=.5,xpd=F)
}
for(i in 1:nrow(rs) ){
  lines(c(0,ncol(rs)+0.5),c(i,i),col="grey95",lwd=.5,xpd=F)
}
points(sort(rep(1:ncol(rs),nrow(rs))),
      rep(nrow(rs):1,ncol(rs)),
        col=colorRampPalette(c("navy","grey95","firebrick"))(91)[cut( c(rs) , breaks = seq(-1,1,length.out = 92) )],pch=16 ,
      cex= sizes*2 + 0.2)
srt=90
text(1:ncol(rs), par("usr")[3] - (par("usr")[4])/200, labels = colnames(rs), srt = srt,
     adj = c(ifelse(srt==0,.5,ifelse(srt==90,1,1)),ifelse(srt==0,1,ifelse(srt==90,.5,1))),
     xpd = TRUE, cex=1)
add_letter(figlabels[1]); figlabels <- figlabels[-1]
}

empty_plot(xlim=c(.5,ncol(rs)+.5),ylim=c(.5,nrow(rs)+.5),xaxs="i",yaxs="i")
text(par("usr")[1] , 1:nrow(rs) , labels = rownames(rs), srt = 0, adj = c(0,0.5), xpd = TRUE, cex=1)

add_scale_legend(pal = colorRampPalette(c("grey90","firebrick"))(91),labels = c("0","0.5","1"))
add_size_legend(labels = c("> 0.01","< 1e-5","< 1e-8","< 1e-11"),max.cex = 2.2, min.cex = .2)

## Figure S2 v3

```{r, echo = FALSE, eval = TRUE, fig.asp=.5}
metadata_parameters <- colnames(metadata)[-c(1:2)]

set.seed(1)
noise <- matrix(rnorm(prod(dim(clean_Ftest)),mean = 0,sd = 1e-10),nrow(clean_Ftest),ncol(clean_Ftest))
o <- hclust(as.dist( (1-cor(clean_Ftest+noise)/2) ),method = "ward.D2")$order

sizes <- as.matrix(-log10(clean_Ftest))
# sizes[sizes < 2] <- 0
sizes[sizes > 7] <- 7
sizes <- sizes / max(sizes)
sizes <- sizes * lower.tri(sizes)

mypar(1,1,mar=c(10,10,2,6))
plot(0,0, las=1,xlim=c(.5,ncol(sizes)+.5),ylim=c(.5,nrow(sizes)+.5),
       axes=F,ylab="",xlab="",main="",xaxs="i",yaxs="i", frame=T)
for(i in 1:ncol(sizes)){
  lines(c(i,i),c(nrow(sizes)+.5,0),col="grey95",lwd=.5,xpd=F)
}
for(i in 1:nrow(sizes) ){
  lines(c(0,ncol(sizes)+0.5),c(i,i),col="grey95",lwd=.5,xpd=F)
}
points(sort(rep(1:ncol(sizes),nrow(sizes))),
      rep(nrow(sizes):1,ncol(sizes)),
        col=colorRampPalette(c("grey95","orange3","firebrick","black"))(91)[cut( c(sizes) , breaks = seq(0,1,length.out = 92) )],pch=16 ,
      cex= sizes*1 + 0.2)
srt=90
text(1:ncol(sizes), par("usr")[3] - (par("usr")[4])/200, labels = colnames(sizes), srt = srt,
     adj = c(ifelse(srt==0,.5,ifelse(srt==90,1,1)),ifelse(srt==0,1,ifelse(srt==90,.5,1))),
     xpd = TRUE, cex=1)
text(par("usr")[1] , 1:nrow(sizes) , labels = rownames(sizes), srt = 0, adj = c(1,0.5), xpd = TRUE, cex=1)

add_scale_legend(pal = colorRampPalette(c("grey95","orange3","firebrick","red"))(91),labels = c("> 0.01","< 1e-5","< 1e-8","< 1e-11"))
add_size_legend(labels = c("> 0.01","< 1e-5","< 1e-8","< 1e-11"),max.cex = 1.2, min.cex = .2)
```

@@

## Figure S7

```{r, echo = FALSE, eval = TRUE,fig.asp=1.2}
figlabels <- letters
mypar(3,3,mar=c(4,10,2,2))
for( j in c("ASV_tissue_V3_normalized_batch_corrected",
        "ASV_CVL_V3_normalized_batch_corrected",
        "ASV_CVL_V2_normalized_NOT_batch_corrected")){
  temp_group <- as.character(group_annotation)
  temp_group[ is.na(temp_group) ] <- "NA"
  temp_group[ temp_group == "" ] <- "NA"
  temp_group <- factor(temp_group)

  plot_dots(data=module_means_per_dataset[[j]],srt=45,
          genes=rownames(module_means_per_dataset[[j]]),col = pal,
          clustering=temp_group, main=paste0(sub("_norm.*","",j)))
  add_letter(figlabels[1]); figlabels <- figlabels[-1]
  empty_plot()
  empty_plot()
}
```

## Figure S8

```{r, echo = FALSE, eval = TRUE,fig.asp=1.2}
mypar(mar=c(10,6,1,1))

top_all <- lapply( datasets_all_samples[2:4] , function(x){
   sort(apply(x,1,var),decreasing = T)[1:20]} )
top <- unique( sub( ".*[.]" , "" , names(unlist(top_all)) ) )

x <- t(sapply(datasets_all_samples[2:4],function(x){
  c(t(x))
}))
colnames(x) <- c(sapply(rownames(datasets_all_samples[[2]]),
                        function(i){rep(i,ncol(datasets_all_samples[[2]]))}))
rownames(x) <- gsub("ASV_|_norm.*", "",rownames(x))

top <- sort(sapply( unique(colnames(x)),
               function(i) { mean( x[,colnames(x)==i ] ) } ),decreasing = T)
top <- names(top)[1:30]

violist(data = x[,colnames(x)%in%top],
        genes = rownames(x),
        clustering = factor( colnames(x)[colnames(x)%in%top],levels = top) ,
        srt=45,
        transparency = 50,col = pal)
```

## Figure S9

```{r, echo = FALSE, eval = TRUE,fig.asp=1.2}

### 2021-02-23 reports/rmarkdown/manuscript/manuscript_template.tex
add metadata association and KEGG for TRX

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{February 20, 2021}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-7-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-7-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-7-3}

@@

@@

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-11-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-11-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-11-3}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-12-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-12-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-12-3}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-13-1}

>>>>

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{February 23, 2021}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-7-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-7-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-7-3}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-7-4}

@@

\hypertarget{figure-s2-v2}{%
\subsection{Figure S2 v2}\label{figure-s2-v2}}

@@

\hypertarget{figure-s2-v3}{%
\subsection{Figure S2 v3}\label{figure-s2-v3}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-11-1}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-12-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-13-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-13-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-13-3}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-14-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-14-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-14-3}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-15-1}

\hypertarget{figure-s7}{%
\subsection{Figure S7}\label{figure-s7}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-16-1}

\hypertarget{figure-s8}{%
\subsection{Figure S8}\label{figure-s8}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-17-1}

\hypertarget{figure-s9}{%
\subsection{Figure S9}\label{figure-s9}}
